Application of Machine Learning to Predict the Optoelectronic Properties of Benzobisazoles

### 2014-06-06 paper/paper.tex
Change paper to use eps images instead of png
Update paper

\documentclass[titlepage]{article}
\usepackage{graphicx}       % include figures
\usepackage{float}          % align figures
\usepackage{amsmath}        % \pm
% \usepackage{indentfirst}
\usepackage{achemso}
\usepackage[bf]{caption}    % bold figure names
\usepackage{url}
\usepackage{setspace}
\restylefloat{table}        % same page tables
\usepackage{chngpage}
\usepackage{multirow}

@@

\title{Application of Machine Learning Methods to the Optoelectronic properties of Benzobisazoles}
\author{Christopher Collins}

@@

\doublespace
\section{Introduction}

Organic solar cell stuff, cruiform stuff, machine learning stuff

@@

The naming scheme is broken down into three separate components. These parts are the core, the sides, and the options.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=1.25in]{TXY.png}
  \end{center}
  \caption{TXY Core}
  \label{fig:txy}
\end{figure}

The core is the central part of the molecule. All cores are identified by a combination of three letters. The first letter indicates whether or not the structure is Cis or Trans which correspond to the letters C and T respectively. The second letter in the core name is the symbol for the element that is in the core without the $\pi$ bond (meh?) (for consistency in naming this will always be the top right atom). This can be one of O, S, N, P, or C. The final letter is the remaining element's symbol which can be N, P, or C (for consistency this will always be the bottom right atom).

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=1.25in]{CXY.png}
  \end{center}
  \caption{CXY Core}
  \label{fig:cxy}
\end{figure}

@@

\begin{table}[H]
  \centering
  \caption{Aryl Groups}
  \begin{tabular}{ccc}
    Label   & Name          & Structure \\
    \hline
    2       & Double Bond   &           \\
    3       & Triple Bond   &           \\
    4       & Phenyl        &           \\
    5       & Thiophene     &           \\
    6       & Pyridine      &           \\
    7       & Carbazole     &           \\
    8       & TZ            &           \\
    9       & EDOT          &           \\
    \hline
  \end{tabular}
  \label{tab:aryl}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{X/R-Groups}
  \begin{tabular}{ccc}
    Label   & Name          & Structure \\
    \hline
    A/a     & Hydrogen  &           \\
    B/b     & Chlorine  &           \\
    C/c     & Bromine   &           \\
    D/d     & CN        &           \\
    E/e     & CCH       &           \\
    F/f     & OH        &           \\
    G/g     & SH        &           \\
    H/h     & $NH_2$    &           \\
    I/i     & $CH_3$    &           \\
    J/j     & Phenyl    &           \\
    K/k     & TMS       &           \\
    L/l     & $OCH_3$   &           \\
    *       & Spacer    &           \\
    \hline
  \end{tabular}
  \label{tab:xrgroups}
\end{table}

@@

@@

\section{Methods}
\subsection{Mean Value}
\subsection{Linear Regression}
\subsubsection{Regular}
\subsubsection{Ridged}
\subsection{Tree}
\subsection{k-Nearest Neighbors}
\subsection{Support Vector Machines}

% \begin{figure}[H]
%   \begin{center}
%     \includegraphics[width=5in]{scan2.png}
%   \end{center}
%   \caption{Scan of SVM parameters C and gamma}
%   \label{fig:homolumo}
% \end{figure}

\subsubsection{Gaussian Kernel}
$$ k(x, x') = exp\left( −\frac{1}{2\sigma^2} \lVert x - x'  \rVert^2 \right) $$

\subsubsection{Laplacian Kernel}
$$ k(x, x') = exp\left( −\frac{1}{\sigma} \lvert x - x' \rvert \right) $$

@@

Roughly 1100 benzobisazole structures were built (using a script?). Once they were built the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31(g). After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31(g).

@@

(When to mention Decay with Prediction creation?)

Once all the data and feature vectors were collected, the machine learning stuff...

For each feature vector, property, method set the methods relevant parameters were optimized (C, gamma, max depth, alpha, n neighbors). Then using these optimized parameters, the machine learning models were trained using k-folds specifically using 10 folds (bla bla).

(maybe invert the procedure)

@@

\begin{table}[H]
  \centering
  \caption{Band Gap Results}
  \begin{tabular}{lll}
            Feature Vector     & Method       & MAE (eV)                \\
    \hline\hline
    \multirow{7}{*}{Naive}     & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.2628 $\pm$ 0.019 \\
                               & Linear Ridge & 0.2571 $\pm$ 0.020 \\
                               & Tree         & 0.1429 $\pm$ 0.016 \\
                               & k-NN         & 0.2096 $\pm$ 0.018 \\
                               & SVM Gauss    & \textbf{0.1355 $\pm$ 0.011} \\
                               & SVM Laplace  & 0.1681 $\pm$ 0.013 \\
    \hline
    \multirow{7}{*}{Decay}     & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.2531 $\pm$ 0.022 \\
                               & Linear Ridge & 0.2506 $\pm$ 0.023 \\
                               & Tree         & 0.1318 $\pm$ 0.018 \\
                               & k-NN         & 0.2112 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.1297 $\pm$ 0.011} \\
                               & SVM Laplace  & 0.1591 $\pm$ 0.011 \\
    \hline
    \multirow{7}{*}{Decay with Length Corrections} & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.2485 $\pm$ 0.020 \\
                               & Linear Ridge & 0.2466 $\pm$ 0.020 \\
                               & Tree         & 0.1492 $\pm$ 0.029 \\
                               & k-NN         & 0.2169 $\pm$ 0.013 \\
                               & SVM Gauss    & \textbf{0.1314 $\pm$ 0.011} \\
                               & SVM Laplace  & 0.1631 $\pm$ 0.011 \\
    \hline
    \multirow{7}{*}{Decay with Predictions} & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.1211 $\pm$ 0.011 \\
                               & Linear Ridge & 0.1174 $\pm$ 0.010 \\
                               & Tree         & 0.1369 $\pm$ 0.012 \\
                               & k-NN         & 0.1724 $\pm$ 0.015 \\
                               & SVM Gauss    & \textbf{0.1004 $\pm$ 0.010} \\
                               & SVM Laplace  & 0.1154 $\pm$ 0.009 \\
    \hline\hline
  \end{tabular}
  \label{tab:gapresults}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{HOMO Results}
  \begin{tabular}{lll}
            Feature Vector     & Method       & MAE (eV)                \\
    \hline\hline
    \multirow{7}{*}{Naive} & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.2002 $\pm$ 0.024 \\
                               & Linear Ridge & 0.1949 $\pm$ 0.024 \\
                               & Tree         & 0.1546 $\pm$ 0.012 \\
                               & k-NN         & 0.2449 $\pm$ 0.025 \\
                               & SVM Gauss    & \textbf{0.1126 $\pm$ 0.014} \\
                               & SVM Laplace  & 0.1557 $\pm$ 0.016 \\
    \hline
    \multirow{7}{*}{Decay}     & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.1868 $\pm$ 0.025 \\
                               & Linear Ridge & 0.1860 $\pm$ 0.025 \\
                               & Tree         & 0.1455 $\pm$ 0.017 \\
                               & k-NN         & 0.2549 $\pm$ 0.026 \\
                               & SVM Gauss    & \textbf{0.1069 $\pm$ 0.010} \\
                               & SVM Laplace  & 0.1431 $\pm$ 0.014 \\
    \hline
    \multirow{7}{*}{Decay with Length Corrections} & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.1883 $\pm$ 0.024 \\
                               & Linear Ridge & 0.1875 $\pm$ 0.025 \\
                               & Tree         & 0.1453 $\pm$ 0.021 \\
                               & k-NN         & 0.2622 $\pm$ 0.028 \\
                               & SVM Gauss    & \textbf{0.1082 $\pm$ 0.012} \\
                               & SVM Laplace  & 0.1457 $\pm$ 0.017 \\
    \hline
    \multirow{7}{*}{Decay with Predictions} & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.0904 $\pm$ 0.007 \\
                               & Linear Ridge & 0.0897 $\pm$ 0.008 \\
                               & Tree         & 0.1439 $\pm$ 0.016 \\
                               & k-NN         & 0.1734 $\pm$ 0.020 \\
                               & SVM Gauss    & \textbf{0.0852 $\pm$ 0.007} \\
                               & SVM Laplace  & 0.1001 $\pm$ 0.008 \\
    \hline\hline
  \end{tabular}
  \label{tab:gapresults}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{LUMO Results}
  \begin{tabular}{lll}
            Feature Vector     & Method       & MAE (eV)                \\
    \hline\hline
    \multirow{7}{*}{Naive}     & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1900 $\pm$ 0.028 \\
                               & Linear Ridge & 0.1862 $\pm$ 0.025 \\
                               & Tree         & 0.1529 $\pm$ 0.007 \\
                               & k-NN         & 0.2351 $\pm$ 0.019 \\
                               & SVM Gauss    & \textbf{0.1055 $\pm$ 0.010} \\
                               & SVM Laplace  & 0.1454 $\pm$ 0.014 \\
    \hline
    \multirow{7}{*}{Decay}     & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1816 $\pm$ 0.026 \\
                               & Linear Ridge & 0.1801 $\pm$ 0.026 \\
                               & Tree         & 0.1510 $\pm$ 0.024 \\
                               & k-NN         & 0.2323 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.1022 $\pm$ 0.015} \\
                               & SVM Laplace  & 0.1317 $\pm$ 0.012 \\
    \hline
    \multirow{7}{*}{Decay with Length Corrections} & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1847 $\pm$ 0.027 \\
                               & Linear Ridge & 0.1828 $\pm$ 0.027 \\
                               & Tree         & 0.1540 $\pm$ 0.023 \\
                               & k-NN         & 0.2348 $\pm$ 0.014 \\
                               & SVM Gauss    & \textbf{0.1029 $\pm$ 0.012} \\
                               & SVM Laplace  & 0.1331 $\pm$ 0.012 \\
    \hline
    \multirow{7}{*}{Decay with Predictions} & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1233 $\pm$ 0.012 \\
                               & Linear Ridge & 0.0877 $\pm$ 0.011 \\
                               & Tree         & 0.0863 $\pm$ 0.010 \\
                               & k-NN         & 0.1699 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.0792 $\pm$ 0.009} \\
                               & SVM Laplace  & 0.0922 $\pm$ 0.009 \\
    \hline\hline
  \end{tabular}
  \label{tab:gapresults}
\end{table}

@@

BLOB
Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors. The optimized paramters for the ... $C \approx 10$ and $\gamma \approx 0.05$.

@@

Unexpectedly, the decay function with distance corrections did not perform any better than the regular decay feature vector. In theory, this should have worked better with hetrogenous side chains...

@@

None of the feature vectors take into account the kuhn expression for polymer chains. This leads to high errors as n or m > 1. The problem is not as pronounced when using SVM with Gaussian kernels because of how they decay (?).

%        Neural Network
%            Tested various network configurations and could the best MAE was around 0.20 eV
%            Network configuration seemed to have minimal impact on results
%            Problem attributed to inexperience with Neural Networks

>>>>

% \documentclass[10pt,twocolumn]{article}
\documentclass[10pt]{article}
\usepackage{graphicx}       % include figures
\usepackage{float}          % align figures
\usepackage{amsmath}        % \pm
% \usepackage{indentfirst}
\usepackage{achemso}
\usepackage[bf]{caption}    % bold figure names
\usepackage{url}
\usepackage{setspace}
\restylefloat{table}        % same page tables
\usepackage{chngpage}
\usepackage{multirow}
% \graphicspath{ {./figures/} }

@@

\title{Application of Machine Learning to Predict the Optoelectronic Properties of Benzobisazoles}
\author{Christopher Collins}

@@

\begin{abstract}
By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively. These results also come with the added benefit of being 30,000,000 times faster than the equivilant Density Functional Theory calculation.
\end{abstract}

% \doublespace
\section{Introduction}

There are many possible molecules that could be used as organic solar cells, the problem is current organic solar cells have poor effeciency [CITE]. Computational

Because of these problems, there is a need to rapidly predict the properties of molecules so that. Machine learning has been shown to be a fast way to predict properties of many systems and specifically, has been shown to be a viable way to predict properties of molecules\cite{hansen_assessment_2013} \cite{montavon_machine_2013}.

For this study, we will be looking at using different machine learning methods in conjunction with Density Functional Theory calculations to be able to predict the

@@

To be able to represent these molecular structures to the machine learning algorthims, a common naming scheme was formed such that it could be reaily converted into a vector form. This naming scheme exploits the planar nature of benzobisazoles as well as their cruxiformic structure.
The naming scheme is broken down into three separate components. These parts are the core, the sides, and the options.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=1.25in]{figures/TXY.png}
  \end{center}
  \caption{TXY Core}
  \label{fig:txy}
\end{figure}

The core is the central part of the molecule. All cores are identified by a combination of three letters. The first letter indicates whether or not the structure is Cis or Trans which correspond to the letters C and T respectively. The second letter in the core name is the symbol for the element that is in the core without the $\pi$ bond (meh?) (for consistency in naming this will always be the top right atom). This can be one of Oxygen (O), Sulfur (S), Nitrogen (N), Phosporous (P), or Carbon (C). The final letter is the remaining element's symbol which can be N, P, or C (for consistency this will always be the bottom right atom).

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=1.25in]{figures/CXY.png}
  \end{center}
  \caption{CXY Core}
  \label{fig:cxy}
\end{figure}

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=1.75in]{figures/aryl.png}
  \end{center}
  \caption{Aryl Groups}
\end{figure}

\begin{table}[H]
  \centering
  \caption{Aryl Groups}
  \begin{tabular}{lc}
    Label   & Name                    \\
    \hline
    2       & Double Bond             \\
    3       & Triple Bond             \\
    4       & Phenyl                  \\
    5       & Thiophene               \\
    6       & Pyridine                \\
    7       & Carbazole               \\
    8       & Tetrazine               \\
    9       & Ethylenedioxythiophene  \\
    \hline
  \end{tabular}
  \label{tab:aryl}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{X/R-Groups}
  \begin{tabular}{lc}
    Label   & Name      \\
    \hline
    A/a     & Hydrogen  \\
    B/b     & Chlorine  \\
    C/c     & Bromine   \\
    D/d     & CN        \\
    E/e     & CCH       \\
    F/f     & OH        \\
    G/g     & SH        \\
    H/h     & $NH_2$    \\
    I/i     & $CH_3$    \\
    J/j     & Phenyl    \\
    K/k     & TMS       \\
    L/l     & $OCH_3$   \\
    *       & Spacer    \\
    \hline
  \end{tabular}
  \label{tab:xrgroups}
\end{table}

@@

To be able to represent these structures to the computer, and consequently to the machine learning algorthms they must be vectorized.

@@

\section{Machine Learning Methods}

In previous work \cite{montavon_machine_2013}, it has been shown that different machine learning algorthms have had drastically different performance when used to predict molecular properties. Because of this, seven algorthms were picked to compare. These were mean value, linear regression, linear ridged regression, tree regression, k-nearest neighbors, and support vector machines. The mean value method is used as a baseline for all of the other methods. ()

 \begin{figure}[H]
   \begin{center}
     \includegraphics[width=5in]{figures/surf.png}
   \end{center}
   \caption{Scan of SVM parameters C and $\gamma$}
   \label{fig:scan}
 \end{figure}

@@

Roughly 1100 benzobisazole structures were built. Once they were built the structures were optimized using Density Functional Theory (DFT) with B3LYP/6-31g*. After the optimization, the molecules were then ran with Time Dependent Density Functional Theory (TDDFT) with B3LYP/6-31g*.

@@

Once all the data and feature vectors were collected, they were feed into the machine learning algorthms. For each feature vector, property, method set the methods relevant parameters were optimized (C, $\gamma$, max depth, $\alpha$, n neighbors). Then using these optimized parameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds. All of the results were then tabled and compared based on their mean absolute errors (MAE).

@@

\begin{table}[H]
  \centering
  \caption{Band Gap Results}
  \begin{tabular}{llr}
            Feature Vector     & Method       & MAE (eV)                \\
    \hline\hline
    \multirow{7}{*}{Naive}     & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.2628 $\pm$ 0.019 \\
                               & Linear Ridge & 0.2571 $\pm$ 0.020 \\
                               & Tree         & 0.1429 $\pm$ 0.016 \\
                               & k-NN         & 0.2096 $\pm$ 0.018 \\
                               & SVM Gauss    & \textbf{0.1355 $\pm$ 0.011} \\
                               & SVM Laplace  & 0.1681 $\pm$ 0.013 \\
    \hline
    \multirow{7}{*}{Decay}     & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.2531 $\pm$ 0.022 \\
                               & Linear Ridge & 0.2506 $\pm$ 0.023 \\
                               & Tree         & 0.1318 $\pm$ 0.018 \\
                               & k-NN         & 0.2112 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.1297 $\pm$ 0.011} \\
                               & SVM Laplace  & 0.1591 $\pm$ 0.011 \\
    \hline
    \multirow{7}{*}{Decay with Length Corrections} & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.2485 $\pm$ 0.020 \\
                               & Linear Ridge & 0.2466 $\pm$ 0.020 \\
                               & Tree         & 0.1492 $\pm$ 0.029 \\
                               & k-NN         & 0.2169 $\pm$ 0.013 \\
                               & SVM Gauss    & \textbf{0.1314 $\pm$ 0.011} \\
                               & SVM Laplace  & 0.1631 $\pm$ 0.011 \\
    \hline
    \multirow{7}{*}{Decay with Predictions} & Mean Value   & 0.5051 $\pm$ 0.044 \\
                               & Linear       & 0.1211 $\pm$ 0.011 \\
                               & Linear Ridge & 0.1174 $\pm$ 0.010 \\
                               & Tree         & 0.1369 $\pm$ 0.012 \\
                               & k-NN         & 0.1724 $\pm$ 0.015 \\
                               & SVM Gauss    & \textbf{0.1004 $\pm$ 0.010} \\
                               & SVM Laplace  & 0.1154 $\pm$ 0.009 \\
    \hline\hline
  \end{tabular}
  \label{tab:gapresults}
\end{table}

 \begin{figure}[H]
   \begin{center}
     \includegraphics[width=5in]{figures/gapbars.pdf}
   \end{center}
   \caption{Band Gap Results}
   \label{fig:scan}
 \end{figure}

@@

\begin{table}[H]
  \centering
  \caption{HOMO Results}
  \begin{tabular}{llr}
            Feature Vector     & Method       & MAE (eV)                \\
    \hline\hline
    \multirow{7}{*}{Naive} & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.2002 $\pm$ 0.024 \\
                               & Linear Ridge & 0.1949 $\pm$ 0.024 \\
                               & Tree         & 0.1546 $\pm$ 0.012 \\
                               & k-NN         & 0.2449 $\pm$ 0.025 \\
                               & SVM Gauss    & \textbf{0.1126 $\pm$ 0.014} \\
                               & SVM Laplace  & 0.1557 $\pm$ 0.016 \\
    \hline
    \multirow{7}{*}{Decay}     & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.1868 $\pm$ 0.025 \\
                               & Linear Ridge & 0.1860 $\pm$ 0.025 \\
                               & Tree         & 0.1455 $\pm$ 0.017 \\
                               & k-NN         & 0.2549 $\pm$ 0.026 \\
                               & SVM Gauss    & \textbf{0.1069 $\pm$ 0.010} \\
                               & SVM Laplace  & 0.1431 $\pm$ 0.014 \\
    \hline
    \multirow{7}{*}{Decay with Length Corrections} & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.1883 $\pm$ 0.024 \\
                               & Linear Ridge & 0.1875 $\pm$ 0.025 \\
                               & Tree         & 0.1453 $\pm$ 0.021 \\
                               & k-NN         & 0.2622 $\pm$ 0.028 \\
                               & SVM Gauss    & \textbf{0.1082 $\pm$ 0.012} \\
                               & SVM Laplace  & 0.1457 $\pm$ 0.017 \\
    \hline
    \multirow{7}{*}{Decay with Predictions} & Mean Value   & 0.4330 $\pm$ 0.038 \\
                               & Linear       & 0.0904 $\pm$ 0.007 \\
                               & Linear Ridge & 0.0897 $\pm$ 0.008 \\
                               & Tree         & 0.1439 $\pm$ 0.016 \\
                               & k-NN         & 0.1734 $\pm$ 0.020 \\
                               & SVM Gauss    & \textbf{0.0852 $\pm$ 0.007} \\
                               & SVM Laplace  & 0.1001 $\pm$ 0.008 \\
    \hline\hline
  \end{tabular}
  \label{tab:homoresults}
\end{table}

 \begin{figure}[H]
   \begin{center}
     \includegraphics[width=5in]{figures/homobars.pdf}
   \end{center}
   \caption{HOMO Results}
   \label{fig:scan}
 \end{figure}

@@

\begin{table}[H]
  \centering
  \caption{LUMO Results}
  \begin{tabular}{llr}
            Feature Vector     & Method       & MAE (eV)                \\
    \hline\hline
    \multirow{7}{*}{Naive}     & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1900 $\pm$ 0.028 \\
                               & Linear Ridge & 0.1862 $\pm$ 0.025 \\
                               & Tree         & 0.1529 $\pm$ 0.007 \\
                               & k-NN         & 0.2351 $\pm$ 0.019 \\
                               & SVM Gauss    & \textbf{0.1055 $\pm$ 0.010} \\
                               & SVM Laplace  & 0.1454 $\pm$ 0.014 \\
    \hline
    \multirow{7}{*}{Decay}     & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1816 $\pm$ 0.026 \\
                               & Linear Ridge & 0.1801 $\pm$ 0.026 \\
                               & Tree         & 0.1510 $\pm$ 0.024 \\
                               & k-NN         & 0.2323 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.1022 $\pm$ 0.015} \\
                               & SVM Laplace  & 0.1317 $\pm$ 0.012 \\
    \hline
    \multirow{7}{*}{Decay with Length Corrections} & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1847 $\pm$ 0.027 \\
                               & Linear Ridge & 0.1828 $\pm$ 0.027 \\
                               & Tree         & 0.1540 $\pm$ 0.023 \\
                               & k-NN         & 0.2348 $\pm$ 0.014 \\
                               & SVM Gauss    & \textbf{0.1029 $\pm$ 0.012} \\
                               & SVM Laplace  & 0.1331 $\pm$ 0.012 \\
    \hline
    \multirow{7}{*}{Decay with Predictions} & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1233 $\pm$ 0.012 \\
                               & Linear Ridge & 0.0877 $\pm$ 0.011 \\
                               & Tree         & 0.0863 $\pm$ 0.010 \\
                               & k-NN         & 0.1699 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.0792 $\pm$ 0.009} \\
                               & SVM Laplace  & 0.0922 $\pm$ 0.009 \\
    \hline\hline
  \end{tabular}
  \label{tab:gapresults}
\end{table}

 \begin{figure}[H]
   \begin{center}
     \includegraphics[width=5in]{figures/lumobars.pdf}
   \end{center}
   \caption{LUMO Results}
   \label{fig:scan}
 \end{figure}

@@

Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors. The optimized paramters for the method were $C \approx 10$ and $\gamma \approx 0.05$.

@@

Unexpectedly, the decay function with distance corrections did not perform any better than the regular decay feature vector. In theory, this should have worked better with hetrogenous side chains, but its use seemed to only increase the MAE.

@@

To run the original DFT and TDDFT calculations for these moelcules took about 35,0000 CPU hours. Calculating the same properties using these machine learning methods took about 4 seconds.

% In addition to the machine learning methods used in this study, there was also an attempt to use Neural Networks for the predictions. Unfortunatly, the results were not satisfactory relative to the amount of time required (0.20 eV MAE). Drastic changes to the network made minimal differences to the final error. This is attirbuted to inexperience with proper methodologies with Neural Networks.

\section{Future Work}

Continue making tweaks to reduce error
Collect more data

None of the feature vectors take into account the kuhn expression for polymer chains. This leads to high errors as n or m > 1. The problem is not as pronounced when using SVM with Gaussian kernels because of how they decay (?). Preliminary work with this addition corrected seems to be the best way to account for polymerization of benzobisazoles.
Test with additional properties (total energy, dipole, etc.)
Generalize for any structure
Make it faster
% In addition to the machine learning methods used in this study, there was also an attempt to use Neural Networks for the predictions. Unfortunatly, the results were not satisfactory relative to the amount of time required (0.20 eV MAE). Drastic changes to the network made minimal differences to the final error. This is attirbuted to inexperience with proper methodologies with Neural Networks.
